Why Donors Donate?

### 2020-09-10 analysis/05_market_simulator.Rmd
Only need to check a few of the hold out levels for the inputs

# Need to Fix
selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Few times a year",
                     "Once a year",
                     "Never"))

# Need to Fix
selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

@@

# Need to Fix
selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("Very little Trust"))

# Double Check this one
selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Rarely',
                     'Atleast once a month'))

@@

# Need to Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't Volunteered",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

# Need to Fix
selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not Involved',
                     'Involved'))

# Need to Fix
selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Not Involved',
                     'Involved'))

# Need to Fix
selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

@@

# Need to Fix
selectInput("p1_education",
         label = "Education:",
         choices = c("Less than Highschool",
                     "Highschool Graduate",
                     "Some College",
                     "2 Year College",
                     "4 Year College",
                     "Graduate or Professional Degree",
                     "Doctorate"))
# Need to Fix
selectInput("p1_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     'More than Median (>$61,372)'))

@@

# Need to Fix
selectInput("p1_age",
         label = "Age:",
         choices = c('Less than Median Age (< 36)',
                     "More than Median Age (> 36)"))

>>>>

# Need to check hold out level
selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust"))

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly Agree"))

# Need to check hold out 
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Never",
                     "Rarely",
                     "At least once a month"))

# Need to check hold out
selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"))

@@

# Need to check hold out level
selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("Hold out",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"))

# Need to check hold out level
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust"))

# Need to check hold out level
selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Rarely',
                     'Atleast once a month'))

@@

# Need to check hold out level
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

@@

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than highschool",
                     "Highschool graduate",
                     "Some college",
                     "2 year college",
                     "4 year college",
                     "Graduate or professional degree",
                     "Doctorate"))

selectInput("p1_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'))

@@

selectInput("p1_age",
         label = "Age:",
         choices = c('Less than median age of 36',
                     "More than median age of 36"))
